Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
add @benmarwick
update addresses

      - Buffalo, New York, 14263, USA

@@

      - Bellevue, WA, 98006

@@

      - RStudio

@@

      - Boston, MA 02210

@@

@@

      - 413 19 Gothenburg

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised the full first draft.
CB ..
RC and EH wrote the section on interfaces for Docker in R.
DE wrote the introduction and section about Rocker.
ME ..
CF wrote the paragraphs about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
DB wrote the section on \pkg{outsider}.
All authors approved the final version.

>>>>

      - Buffalo, NY, 14263, USA

@@

      - Bellevue, WA, 98006, USA

@@

@@

      - Boston, MA 02210, USA

@@

    # https://github.com/benmarwick/
    affiliation: University of Washington
      - Department of Anthropology
      - Denny Hall 230, Spokane Ln
      - Seattle, WA 98105, USA
      - \orcid{0000-0001-7879-4531}
    email: bmarwick@uw.edu

@@

      - 413 19 Gothenburg, Sweden

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote sections not mentioned below, and revised all sections.
DE wrote the introduction and section about Rocker.
CB ..
RC and EH wrote the section on interfaces for Docker in R.
ME ..
CF wrote the paragraphs about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW wrote the section on research compendia and made the project Binder-ready.
KR ..
NR ..
NX wrote the section on \pkg{liftr}.
LS \& NT wrote the section on Bioconductor.
DB wrote the section on \pkg{outsider}.
All authors approved the final version.
